%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Winson}{Luk}
\position{University of California, San Diego{\enskip\cdotp\enskip}B.S. Computer Engineering}
\address{San Mateo, CA 94065}

\mobile{(650) 302-3189}
\email{winson@luk.cc}
\homepage{winsonluk.com}
%\github{winsonluk}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {COMPANY}
  {ADDRESS\\CITY, STATE ZIP}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Summer 2018 ROLE Application}
% How the letter is opened
\letteropening{}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a rising junior at UC San Diego majoring in computer engineering. I was born and raised in the San Francisco Bay Area, where my family still lives. Growing up in the heart of Silicon Valley, I spent my early years tinkering with technology from operating systems to websites, and I never stopped. These experiences shaped my interest in software development, providing me with a extremely solid technical background that form the basis of my desire to work for COMPANY.

In high school I elevated my passion for technology from a hobby to an ambition. I was extremely successful in founding and managing an engineering design organization at my school. For three years I directed multiple student teams in their efforts to compete in the San Jose Tech Challenge, helping our school win a total of four regional awards. I committed to the entire operational spectrum of my organization, from technical guidance and oversight all the way through compliance and executive management.

Since then, I have acquired substantial experience as an intern in diverse professional environments. During my senior year at high school, I worked as a content designer for a local tutoring firm to architect a full-length mathematics workbook. I spent my last summer as an intern at Synopsys, a S\&P 500 technology company headquartered in Mountain View, California. At Synopsys, I architected a Perl command line interface that automates ticket creation for Synopsys's global IT operations, and took the initiative to overhaul the existing automation system with an object-oriented approach that significantly reduced time-consuming API calls by over 70\%. My experiences here have refined my skills in communication and problem solving while helping me confirm my enthusiasm to apply my skills as a summer intern at COMPANY.

\lettersection{Why COMPANY?}

As a student who has excelled in courses ranging from psychology to economics to international relations, I value the diverse pursuits of COMPANY and hope to utilize my skills in technology with responsibilities outside the code base. With a track record of succeeding in both hands-on implementations as an engineer and important decision making as a manager, I have the knowledge and experience to strike the correct balance between technological and professional needs. Technically, I am fascinated by the ever more valuable data that COMPANY manages and collects, and I am eager to learn the specialized implementations behind COMPANY's robust technological infrastructure. And since it is clear that COMPANY has ambitious aspirations to make meaningful impacts with technology, as a summer intern I will cherish the responsibility to contribute towards that vision.

I also value the coordination between different roles within an organization, and I respect the inherent need to cooperate between teams to reduce risks and increase efficiency. I would really hope to come to work every day to a place where I know not only are my skills valued, but my personal philosophies as well. And after reflecting on your noble mission and admirable employee culture, I am absolutely confident that I would be an excellent fit as an intern at your CITY office.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
